\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\newcommand{\resumeEducationSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeExperienceSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\textit{#1}}, \textbf{#2} & \textit{#3} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{
  \item \textbf{#1} \small{#2} \vspace{-6pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Language Typeset
\def\CPlusPlus{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}
\def\CSharp{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf \#}}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\LARGE Tien Thuy Ho}
\end{center}

\vspace{-4pt}

\begin{tabularx}{\textwidth} {
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
 (803) 741-6063 & 200 W 60th St., Apt. 25E & \href{http://github.com/thuytien140894}github.com/thuytien140894 \\
 \href{mailto:thuytien140894@gmail.com}thuytien140894@gmail.com & New York, NY 10023 &
 \href{http://linkedin.com/in/hotien}linkedin.com/in/hotien
\end{tabularx}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {M.S. Computer Science;  GPA: 4.0/4.0}{09/2017 -- 06/2018}

    \vspace{-4pt}

    \resumeEducationSubheading
      {University of South Carolina, Honors College}{Columbia, SC}
      {B.S. Computer Science and Mathematics, French Minor;  GPA: 4.0/4.0}{08/2013 -- 05/2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExperienceSubheading
      {Senior iOS Software Engineer}{EBAY}{08/2018 -- Present}
      \resumeItemListStart
        \resumeItem
          {Responsible for building reusable UI components in both UIKit and SwiftUI, and internal developer tools.
          Collaborated closely with principal iOS architects, domain engineers, and designers to ensure
          quality and consistency in user interface and experience. Established best practices through technical presentations 
          and documentation to increase standardization, confidence, and testability across the eBay app. }
        \resumeItem
          {Implemented a Swift tool using Swift Package Manager APIs to download and localize third-party packages. 
          This tool allows engineers to benefit from popular, well-supported third-party solutions 
          for their feature development without the security risks of using remote packages directly through Xcode.}
        \resumeItem
          {Refactored the implementation of SwiftUI sheets, UIKit form, and collection view components
          in order to modernize the codebase and reduce tech debt. Advocated for protocol-oriented practices and 
          small/reusable views to make these components more composable and scalable.}
        \resumeItem
          {Led the development of feature toggles to increase confidence in continuous delivery and data-driven features. 
          Also implemented social registration, package tracking, and local pickup experience to improve user engagement and 
          buying/selling experience.}
      \resumeItemListEnd

    \resumeExperienceSubheading
      {Graduate Teaching Assistant}{UNIVERSITY OF CALIFORNIA}{09/2017 -- 06/2018}
      \resumeItemListStart
        \resumeItem
          {Supervised lab sections for introduction to Java programming. Worked with students with little to no prior programming
          experience and helped introduce them to programming and problem solving.}
        \resumeItem
          {Led discussion sections for introduction to algorithmic analysis. Responsible for answering students' online discussion
          questions regarding homework, class lectures, and exam review.}
      \resumeItemListEnd

      \resumeExperienceSubheading
      {Software Engineering Intern}{APPLE}{05/2016 -- 08/2016}
      \resumeItemListStart
        \resumeItem
          {Collaborated with a team of designers and developers to improve a modeling and simulation 3D tool, developed in
          Unreal Engine, and provide the product development team with a prototyping environment to validate their ideas.}
        \resumeItem
          {Developed an I/O feature, written in {\CPlusPlus} and Blueprint, that feeds camera data from a CSV file into the 3D tool to
          validate and adjust camera arrangement, as well as to visualize each camera's scene capture. This feature also enables saving
          updated camera values and scene captures for further development.}
      \resumeItemListEnd

      \resumeExperienceSubheading
      {Software Engineer}{SYSEDA}{01/2015 -- 07/2017}
      \resumeItemListStart
        \resumeItem
          {Worked with a team of 10 developers to port a \CSharp/Silverlight ship simulation application to Qt for cross-platform deployment.
          Also implemented missing features to enhance usability and effectiveness in ship design and
          simulation.}
        \resumeItem
          {Developed, debugged, and maintained a 3D ship design platform using Three.js and other web development libraries including Kendo UI,
          Knockout.js, and Bootstrap. Implemented important features including path finding, arcball rotation, transform gizmo, collision
          detection, dynamic mesh generation, and general CRUD.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem
      {Tetris-SwiftUI:}{Tetris game using Apple newest frameworks, SwiftUI and Combine.}
    \resumeSubItem
      {GTLC:}{Interpreter for the gradually-typed lambda calculus using the eager coercion calculus, implemented in Haskell.}
    \resumeSubItem
      {Safehouse:}{2-player street view game using Google Maps APIs to simulate the classic cat-and-mouse game.}
    \resumeSubItem
      {fChess:}{Online chess game using 2D game framework Phaser.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem
      {Languages:}{Swift, Objective-C, Java, JavaScript, HTML5, CSS, Haskell, \CPlusPlus}
    \resumeSubItem
      {Development Software:}{Xcode, Git, Mac OS, Windows, Unix/Linux, Visual Studio}
    \resumeSubItem
      {Technologies:}{UIKit, SwiftUI, Combine, Angular, Three.js, Knockout.js, Bootstrap, Kendo UI, Firebase}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
